Results

### 2018-08-05 4-results-simus.Rmd
figs with black color

  results %>%
    myggplot(aes(par.causal, AUC_mean, fill = method, color = method)) +
    geom_hline(yintercept = 0.5, linetype = 2) +
    geom_col(position = position_dodge(), alpha = 0.3) +
    geom_errorbar(aes(ymin = AUC_mean - 2 * AUC_boot, ymax = AUC_mean + 2 * AUC_boot),
                  position = position_dodge(width = 0.9), color = "black", width = 0.2) + 
    scale_y_continuous(limits = c(0.5, NA), minor_breaks = 0:20 / 20,
                       oob = scales::rescale_none) +
    labs(x = "Causal SNPs (number and location)", y = "Mean of 100 AUCs",
         fill = "Method", color = "Method") +
    scale_fill_manual(values = methods.color) +
    scale_color_manual(values = methods.color)
}

@@

```{r}
results2 %>%
  filter(par.model == "simple", method %in% c("logit-simple", "PRS-max")) %>%
  mutate(method = c_method_r2(method, thr.r2)) %>%
  group_by_at(c(vars(starts_with("par")), "method")) %>%
  summarise(AUC_mean = mean(AUC), AUC_boot = boot(AUC), N = n()) %>%
  barplot_causal_all()

ggsave("figures/main-AUC-all-r2.pdf", scale = 1/110, width = 1242, height = 951)
```

@@

```{r}
results4 %>%
  filter(method %in% c("logit-simple", "PRS-max")) %>%
  mutate(method = c_method_r2(method, thr.r2)) %>%
  group_by_at(c(vars(starts_with("par")), "method")) %>%
  summarise(AUC_mean = mean(AUC), AUC_boot = boot(AUC), N = n()) %>%
  barplot_causal_all()

>>>>

  results %>%
    myggplot(aes(par.causal, AUC_mean, fill = method, color = method)) +
    geom_hline(yintercept = 0.5, linetype = 2) +
    geom_col(position = position_dodge(), alpha = 0.5, color = "black", size = 1) +
    geom_errorbar(aes(ymin = AUC_mean - 2 * AUC_boot, ymax = AUC_mean + 2 * AUC_boot),
                  position = position_dodge(width = 0.9), color = "black", width = 0.2, size = 1) + 
    scale_y_continuous(limits = c(0.5, NA), minor_breaks = 0:20 / 20,
                       oob = scales::rescale_none) +
    labs(x = "Causal SNPs (number and location)", y = "Mean of 100 AUCs",
         fill = "Method", color = "Method") +
    scale_fill_manual(values = methods.color) +
    scale_color_manual(values = methods.color)
}

@@

```{r}
results2.all.r2 <- results2 %>%
  filter(par.model == "simple", method %in% c("logit-simple", "PRS-max")) %>%
  mutate(method = c_method_r2(method, thr.r2)) %>%
  group_by_at(c(vars(starts_with("par")), "method")) %>%
  summarise(AUC_mean = mean(AUC), AUC_boot = boot(AUC), N = n())

barplot_causal_all(results2.all.r2)

ggsave("figures/supp-AUC-all-r2.pdf", scale = 1/110, width = 1242, height = 951)
```

@@

```{r}
results4 %>%
  filter(method %in% c("logit-simple", "PRS-max")) %>%
  mutate(method = c_method_r2(method, thr.r2)) %>%
  group_by_at(c(vars(starts_with("par")), "method")) %>%
  summarise(AUC_mean = mean(AUC), AUC_boot = boot(AUC), N = n()) %>%
  barplot_causal_all() + 
  geom_col(aes(par.causal, AUC_mean), data = results2.all.r2, 
           position = position_dodge(), color = "black", alpha = 0)
